\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2021-02-09 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.Rmd
fix Makefile

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  fig.pos = 'ht',
  comment = "#>",
  fig.path = "../figures/",
  out.width = "\\textwidth",
   out.extra = "keepaspectratio=true"
)

>>>>

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  fig.pos = 'ht',
  comment = "#>",
  fig.path = "./",
  out.width = "\\textwidth",
   out.extra = "keepaspectratio=true"
)

### 2021-02-09 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.tex
fix Makefile

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/plot-stratified-erspc-data-1} \caption[Population time plots for both treatment arms in the ERSPC dataset]{Population time plots for both treatment arms in the ERSPC dataset. The gray area can be thought of as N=88,232 (control group) and N=71,661 (screening group) rows of infinitely thin rectangles (person-moments). More events are observed at later follow-up times, motivating the use of non-constant hazard models.}\label{fig:plot-stratified-erspc-data}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/erspc-cox-cif-1} \caption{CIFs for control and screening groups in the ERSPC data. In each of the panels, we plot the CIF from the Cox model using \code{survival::survfit} (solid line) and the CIF from the case-base sampling scheme (dashed line) with different functional forms of time. (1) The time variable is excluded (exponential). (2) Linear function of time (Gompertz). (3) The natural logarithm (Weibull). (4) Cubic B-spline expansion of time.}\label{fig:erspc-cox-cif}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/interaction-ERSPC-1} \caption[Estimated hazard ratio and 95\% confidence interval for screening vs]{Estimated hazard ratio and 95\% confidence interval for screening vs. control group as a function of time in the ERSPC dataset. Hazard ratios are estimated from fitting a parametric hazard model as a function of the interaction between a cubic B-spline basis of follow-up time and treatment arm. 95\% confidence intervals are calculated using the delta method. The plot shows that the effect of screening only begins to become statistically apparent by year 7. The 25-60\% reductions seen in years 8-12 of the study suggests a much higher reduction in prostate cancer due to screening than the single overall 20\% reported in the original article.}\label{fig:interaction-ERSPC}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/compPop-1} \caption[Population-time plot for the stem-cell transplant study with both relapse and competing events]{Population-time plot for the stem-cell transplant study with both relapse and competing events.}\label{fig:compPop}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/bmtcrr-risk-1} \caption{\label{fig:compAbsrisk} Absolute risk curve for a fixed covariate profile and the two disease groups. The estimate obtained from case-base sampling is compared to the Kaplan-Meier estimate.}\label{fig:bmtcrr-risk}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/coefplots-1} \caption{\label{fig:cs3lolliPlot} Coefficient estimates from the Cox model (Cox), penalized Cox model using the \pkg{glmnet} package (Pen. Cox), and our approach using penalized case-base sampling (Pen. CB). Only the covariates that were selected by both penalized approaches are shown. The shrinkage of the coefficient estimates for Pen. Cox and Pen. CB occurs due to the $\ell_1$ penalty.}\label{fig:coefplots}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/riskregressionBrier-1} \caption{\label{fig:cs3FinalBrier} Comparison of Cox regression (Cox), penalized Cox regression (Pen. Cox), penalized case-base sampling estimation (Pen. CB), and Kaplan-Meier (K-M). (A)  Probability of death as a function of follow-up time. (B) Brier score as a function of follow-up time, where a lower score corresponds to better performace.}\label{fig:riskregressionBrier}
\end{figure}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./plot-stratified-erspc-data-1} \caption[Population time plots for both treatment arms in the ERSPC dataset]{Population time plots for both treatment arms in the ERSPC dataset. The gray area can be thought of as N=88,232 (control group) and N=71,661 (screening group) rows of infinitely thin rectangles (person-moments). More events are observed at later follow-up times, motivating the use of non-constant hazard models.}\label{fig:plot-stratified-erspc-data}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./erspc-cox-cif-1} \caption{CIFs for control and screening groups in the ERSPC data. In each of the panels, we plot the CIF from the Cox model using \code{survival::survfit} (solid line) and the CIF from the case-base sampling scheme (dashed line) with different functional forms of time. (1) The time variable is excluded (exponential). (2) Linear function of time (Gompertz). (3) The natural logarithm (Weibull). (4) Cubic B-spline expansion of time.}\label{fig:erspc-cox-cif}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./interaction-ERSPC-1} \caption[Estimated hazard ratio and 95\% confidence interval for screening vs]{Estimated hazard ratio and 95\% confidence interval for screening vs. control group as a function of time in the ERSPC dataset. Hazard ratios are estimated from fitting a parametric hazard model as a function of the interaction between a cubic B-spline basis of follow-up time and treatment arm. 95\% confidence intervals are calculated using the delta method. The plot shows that the effect of screening only begins to become statistically apparent by year 7. The 25-60\% reductions seen in years 8-12 of the study suggests a much higher reduction in prostate cancer due to screening than the single overall 20\% reported in the original article.}\label{fig:interaction-ERSPC}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./compPop-1} \caption[Population-time plot for the stem-cell transplant study with both relapse and competing events]{Population-time plot for the stem-cell transplant study with both relapse and competing events.}\label{fig:compPop}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./bmtcrr-risk-1} \caption{\label{fig:compAbsrisk} Absolute risk curve for a fixed covariate profile and the two disease groups. The estimate obtained from case-base sampling is compared to the Kaplan-Meier estimate.}\label{fig:bmtcrr-risk}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./coefplots-1} \caption{\label{fig:cs3lolliPlot} Coefficient estimates from the Cox model (Cox), penalized Cox model using the \pkg{glmnet} package (Pen. Cox), and our approach using penalized case-base sampling (Pen. CB). Only the covariates that were selected by both penalized approaches are shown. The shrinkage of the coefficient estimates for Pen. Cox and Pen. CB occurs due to the $\ell_1$ penalty.}\label{fig:coefplots}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{./riskregressionBrier-1} \caption{\label{fig:cs3FinalBrier} Comparison of Cox regression (Cox), penalized Cox regression (Pen. Cox), penalized case-base sampling estimation (Pen. CB), and Kaplan-Meier (K-M). (A)  Probability of death as a function of follow-up time. (B) Brier score as a function of follow-up time, where a lower score corresponds to better performace.}\label{fig:riskregressionBrier}
\end{figure}
\end{Schunk}
